Source Summaries

### 2020-04-05 paper/sourceSummaries/summary7.tex
Source 7 Dan

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{A} {H}olistic {F}ramework for {O}pen {L}ow-{P}ower {I}nternet of {T}hings {T}echnology {E}cosystems}

@@

\bibentry{hu2018holistic}

@@

\noindent
The authors identify the working framework for low-power Iot ecosystems and find out the principle of driving the future trends in the industry and research community. The  authors also take a look at IoT technology ecosystems to find four primary business models that can lead to the proposed ecosystem framework.

@@

\noindent
The authors used Systems Theory. They observed how IoT ecosystems work with each other to identify a framework that is holistic.

@@

\noindent
The authors found four primary business models for low-power IoT ecosystems which intersect with one another. The first is semiconductor-driven models, the second is data service driven models, the third is a vertical application-driven model, and the fourth is a framework-driven model. Using these four models the authors created a holistic framework for low-power IoT ecosystems.

@@

\noindent
The author’s framework contains two parts in the front plane. The technical IoT building blocks and the common vertical business segments. The horizontal business segments are briefly shown on the top plane of the framework. The architecture plane indicates the various systems following an architecture based on the common IoT building blocks. On the side plane, the commercial and research maker demands are shown as the market driving force of the elements shown on the front plane. The authors concluded that AllJoyn and ARM are the successful IoT ecosystems that fit the previously proposed model and framework.

@@

\noindent
Is there a way to apply this holistic framework to a real world ecosystem? How do you identify a business model in an IoT technology ecosystem to integrate these technologies?
